\documentclass{article}
\linespread{1.3}
\usepackage[margin=50pt]{geometry}
\usepackage{amsmath, amsthm, amssymb, amsthm, tikz, fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\newcommand{\changefont}{\fontsize{15}{15}\selectfont}

\fancypagestyle{firstpageheader}
{
  \fancyhead[R]{\changefont Michael Huang \\ CFRM 415 \\ Homework 1}
}

\begin{document}

\thispagestyle{firstpageheader}

\section*{1.}
{\Large 

Find the accumulated value of \$100 at the end of 20 years:

\subsection*{(a)}

If the annual interest rate is 6\% simple interest \\
\framebox[1.1\width]{\textbf{answer}}

\subsection*{(b)}

If the annual interest rate is 6\% compounded quarterly \\

\subsection*{(c)}

If the annual interest rate is 6\% compounded continuously \\

}

\section*{2.}
{\Large

Find the present value of \$100 to be paid in 20 years

\subsection*{(a)}

If the annual interest rate is 2\% simple interest \\
\framebox[1.1\width]{\textbf{answer}}

\subsection*{(b)}

If the annual interest rate is 2\% compounded semiannually \\

\subsection*{(c)}

If the annual interest rate is 2\% compounded continuously \\

}

\section*{3.}
{\Large 

Find the annual rate of interest at which the accumulated value of \$1000 at the end of 15 years is \$3000

\subsection*{(a)}

If interest is compounded semiannually \\
\framebox[1.1\width]{\textbf{answer}}

\subsection*{(b)}

If interest is compounded continuously \\

}

\section*{4.}
{\Large 

A dealer of questionable repute prices a used car at \$10,000, and it offers a four-year loan at 18\% compounded monthly, where the customer must pay \$250 per month. How much will the down payment be?

}

\section*{5.}
{\Large 

A junk bond pays a semiannual coupon at an 8\% annual with 5 years to maturity, with a face value of \$5000. The market yield is 2\%.

\subsection*{(a)}

Calculate the bond price \\
\framebox[1.1\width]{\textbf{answer}}

\subsection*{(b)}

Calculate the Macaulay Duration of the bond \\

\subsection*{(c)}

The market yield jumps to 2.02\%. What is the approximate change in the bond price? \\

}

\section*{6.}
{\Large 

A 10-year bond paying a semiannual coupon of 3.5\% has been issued and is trading in the market. It has a face value of \$5000 and matures in two years and two months. The market yield is 1.3\%. Calculate the bond price. \\

}

\section*{7.}
{\Large 

Show that the modified duration of a continuously compounded zero coupon bond is equal to its time to maturity. \\

}

\end{document}